---
title: "PhysicoChemicalPropertiesProtein: Calculation of physico-chemical properties of amino acid and protein sequences"
author:
 - name: Thomas Naake
   mail: thomas.naake@embl.de, thomasnaake@googlemail.com
   affiliation: European Molecular Biology Laboratory, Meyerhofstrasse 1, 69117 Heidelberg
package: PhysicoChemicalPropertiesProtein
      
output:  
    BiocStyle::html_document:
        toc_float: true
bibliography: PhysicoChemicalPropertiesProtein-citations.bib
vignette: >
    %\VignetteIndexEntry{Physico-chemical properties of amino acid and protein sequences}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteKeywords{Proteomics, Mass Spectrometry, MS, QC}
    %\VignettePackage{PhysicoChemicalPropertiesProtein-vignette}
    %\VignetteEncoding{UTF-8}
---

```{r style, echo = FALSE, results = 'asis'}
BiocStyle::markdown()
```

```{r env, include=FALSE, echo=FALSE, cache=FALSE}
library("knitr")
opts_chunk$set(stop_on_error = 1L)
suppressPackageStartupMessages(library("PhysicoChemicalPropertiesProtein"))
```

# Introduction {#sec-intro}


# Installation

To install this package, start `R` and enter:

```{r, eval = FALSE}

```

This will install this package and all eventually missing dependencies.

# Questions and bugs {-}

`PhysicoChemicalPropertiesProtein` is currently under active development. 
If you discover any bugs, typos or develop ideas of improving 
`PhysicoChemicalPropertiesProtein` feel free to raise an issue via
[GitHub](https://github.com/tnaake/PhysicoChemicalPropertiesProtein) or 
send a mail to the developer.

# Calculate physico-chemical properties of amino acid sequences

```{r load_PhysicoChemicalPropertiesProtein}
library("PhysicoChemicalPropertiesProtein")
```

## GRAVY Score

```{r gravy, eval = TRUE, echo = TRUE}
aa <- "TEST"
calculateGravyScore(aa = aa)
```

## Isoelectric point

```{r IE_point, eval = TRUE, echo = TRUE}
aa <- "TEST"
calculateIsoelectricPoint(aa = aa, method = "EMBOSS")
```

# Appendix {-}

## Session information {-}

All software and respective versions to build this vignette are listed here:

```{r session,eval=TRUE, echo=FALSE}
sessionInfo()
```

## References

